\beginsong{Maxwell's Silver Hammer}[by={Beatles}]
\beginverse
\[D]Joan was quizzical \[H7]studied metaphysical
\[Emi]science in the home.
\[A7]late nights all alone with a test-tube
\[D]oh-oh-oh-\[A]oh.
Maxwell Edison majoring in medicine
calls her on the phone
"Can I take you out to the pictures
Joa-oa-oa-oan?"
But \[E7]as she's getting ready to go
\[A7]a knock comes on the door.
\endverse
\beginref
\[D]Bang! Bang! Maxwell's silver hammer came
\[E7]down upon her head.
\[A7]Clang! Clang! Maxwell's silver hammer made
\[Emi]sure that \[A7]she was \[D]dead.
\endverse
\beginverse
Back in school again Maxwell plays the fool again 
teacher gets annoyed 
wishing to avoid an unpleasant 
sce-e-e-ene 
she tells Max to stay when the class has gone away 
so he waits behind 
writing 50 times "I must not be 
so-o-o-o." 
But when she turns her back on the boy 
he creeps up from behind. 
\endverse
\beginref
Bang! Bang! \ldots
\endverse
\beginverse
 P.C. Thirty-One said "We caught a dirty one" 
Maxwell stands alone 
painting testimonial pictures 
oh-oh-oh-oh 
Rose and Valerie screaming from the gallery 
say he must go free Maxwell must go free 
the judge does not agree and he tells them 
so-o-o-o 
but as the words are leaving his lips 
a noise comes from behind.
\endverse
\beginref
Bang! Bang! Maxwell's silver hammer 
came down upon his head. 
Clang! Clang! Maxwell's silver hammer 
made sure that he was dead.
\[D]Sil\[F#7/C#]ver \[Hmi]hamm\[D7/A]er\ldots\[G]\[A7/C#]\[D]\[A7/C#]\[D]
\endverse
\endsong